MCC Predictions

### 2018-05-01 stats/ex3_comparisons.Rmd
starting with bda

>>>>

```{r rsa model2}
rsaModel2 <- 'var ObjectPrior = Categorical({vs: all_objects, ps: [0.1666667, 0.1666667, 0.8333333] })

// pragmaticListener({label: "dax", point: 2 })

var addNoise = function(dist, noiseParam){
   Infer({model: function(){ 
      return flip(noiseParam) ? uniformDraw([0, 1]) : sample(dist)
    }
   })
}

var model = function(){
   var noise = uniform(0, 1)
   var modelPredictions = pragmaticListener({label: "dax", point: 2 })
   var noisyModelPredictions = addNoise(modelPredictions, noise)
   map(data, function(d){ 
      observe(noisyModelPredictions, d)
    } )
  return [noise, modelPredictions]
}

model() 
'
```

```{r}

obs_data <- data %>% filter (Change == "Same speaker", Alignment == "Congruent", Experiment =="Novelty") %>% select(correct_inf)

bda <- webppl(
  program_code = paste(rsaUtils, rsaModel2, sep='\n'),
  data = obs_data,
  data_var = "data"
)
